---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r load-targets, include=FALSE}

tar_load(names = c(sims_smry, sims_combined))


```

## Data simulation

__Step 0__: determine which covariates to simulate.

- GRE Score
- GPA
- logit-transformed probability of passing (normally distributed)

An assumption we make is that these three covariates are normally distributed with some correlation between each one (i.e., multivariate normal).

__Step 1__: set the correlation between covariates in the simulated data.

- Between GRE score and GPA = 0.2.
- Between GPA and probability of passing the qualifier exam = 0.2.
- Between GRE score and probability of passing the qualifier exam = <varying>.

_Step 2_: set the mean and standard deviation (SD) of each covariate.

- GRE score: mean = 300, SD = 50
- GPA: mean = 3.0, SD = 0.5
- probability of passing the qualifier exam: mean = <varying>, SD = 0.3

## Data analysis

We consider three different strategies to accept applicants into the program. None of these strategies are realistic, but are used for illustration purposes.

1. Accept everyone. 
1. Accept applicants with GPA ≥ 3.
1. Accept applicants with GRE score ≥ 75th percentile of applicants.

For each strategy, we compute the median probability of passing the exam, the number of people admitted, and the expected number who would pass the exam. 

## Results

```{r}

library(gt)
library(table.glue)

sims_smry |> 
 ungroup() |> 
 mutate(
  strategy = recode(strategy, 
                    'all' = 'Admit all applicants',
                    'gpa_gt_3' = 'Require GPA \u2265 3.0',
                    'gre_gt_75pct' = 'Require GRE \u2265 75th percentile'),
  group = recode(
   paste(corr_gre_pass, base_prob, sep = '_'),
   "0_0.7" = "No GRE effect, baseline probability of passing exam = 70", 
   "0_0.85" = "No GRE effect, baseline probability of passing exam = 85", 
   "0.2_0.7" = "corr(GRE, pass) = 0.2, baseline probability of passing exam = 70", 
   "0.2_0.85" = "corr(GRE, pass) = 0.2, baseline probability of passing exam = 85"
  ),
  across(starts_with("n_"), table_value),
  pass_prob = table_value(100 * pass_prob)
 ) |> 
 select(strategy, group, pass_prob, n_admit, n_pass) |> 
 gt(rowname_col = 'strategy', groupname_col = 'group') |> 
 cols_label(pass_prob = 'Median probability of passing',
            n_admit = 'Number admitted',
            n_pass = 'Expected number to pass') |> 
 cols_align('center')

```

